Procurements of the Canadian Government, Runaway Military Contracts

### 2024-11-28 paper/paper.qmd
added public spending graph

TODO Military Spending Per year

```{r fig-mil-spending}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

>>>>

TODO Military Spending Per year
```{r fig-mil-spending}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

#TODO Make right color

# Convert award_date to Date type and extract the year
df_filtered$award_date <- as.Date(df_filtered$award_date, format = "%Y-%m-%d")
df_filtered$year <- format(df_filtered$award_date, "%Y")

# Filter for military spending (where buyer is "National Defence")
military_df <- df_filtered %>%
  filter(buyer == "National Defence")

# Summarize total spending per year
military_spending_per_year <- military_df %>%
  group_by(year) %>%
  summarize(total_spending = sum(amount, na.rm = TRUE))

# Create the bar chart
ggplot(data = military_spending_per_year, aes(x = year, y = total_spending)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Military Spending Per Year", x = "Year", y = "Total Spending") +
  theme_minimal() +
  scale_y_continuous(labels = dollar_format(prefix = "$")) +
  theme(plot.title = element_text(hjust = 0.5))

TODO Public Services Spending
```{r fig-public-spending}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: template
#| fig-align: center

#TODO Make right color
